\documentclass[a4paper,11pt]{article}

%-------------Preamble------------------------------------

\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{hyperref}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}

\linespread{0.8}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.2cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------


%------Custom commands---------------------------------

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}

\newcommand{\workexp}[4]{
\begin{minipage}[t]{7cm}
\begin{flushleft}
\textbf{#1} \\
\indent \emph{#2}\\
\end{flushleft}
\end{minipage}
\hfill
\begin{minipage}[t]{7cm}
\begin{flushright}
\textbf{#3} \\
\indent #4 \\
\end{flushright}
\end{minipage}
}
%-----------------------------------------------------------


\begin{document}

%-------------Heading-------------------------------------

\begin{minipage}[t]{7cm}
\begin{flushleft}
\large{Ryan Williams} \\
\indent \textbf{ryanwilliams@berkeley.edu} \\
\indent \url{https://github.com/rydub}\\
\end{flushleft}
\end{minipage}
\hfill
\begin{minipage}[t]{7cm}
\begin{flushright}
\large \indent 1745 Bancroft Way \\
\indent Berkeley, CA 94703 \\
\indent \textbf{(860) 309-8602} \\[\lsep]
\end{flushright}
\end{minipage}
\\[0.2cm]
%-----------------------------------------------------------


%-------------Education-----------------------------------
\resheading{\textbf{Education} }\\[\lsep]
\\[-0.5cm]
\begin{itemize}
\item 
\workexp{UC Berkeley---- 3.4 GPA}{Electrical Engineering \& Computer Science}{Aug. 2016 - Present}{}
\\[-0.3cm]
	\begin{itemize}\itemsep \isep
	\item Selected coursework: Embedded Systems Design, Signals \& Systems, Data Structures, Discrete Math \& Probability Theory, Machine Structures.
	\end{itemize}
\end{itemize}
\begin{itemize}
\item 
\workexp{Santa Barbara City College---- 4.0 GPA}{Engineering Transfer}{Aug. 2013 - May 2016}{}
\\[-0.3cm]
	\begin{itemize}\itemsep \isep
	\item Received SBCC Foundation President's Scholarship. Member, Computer Engineering Club.
	\end{itemize}
\end{itemize}


%-----------------------------------------------------------


%--------Work Experience--------------------------------

\resheading{\textbf{Experience} }\\[\lsep]
\\[-0.5cm]
\begin{itemize}
\item 
\workexp{Summer Associate}{NASA Ames Research Center, Mtn View CA}{May 2017 - Present}{}
\\[-0.3cm]
	\begin{itemize}\itemsep \isep
	\item Electronics engineer and researcher working on free space optical communication protocol.
	\item Co-author of NASA invention disclosure and forthcoming technical paper. Designed graphics, and technology demonstration for grant proposals and annual reports.
	\item Develops MATLAB and Python scripts for serial communication (RS-232), waveform generation, and signal processing
	\item Manages set-up, execution, and data processing for optics experiments. Trained in laser safety and conducting experiments that include amplitude and wave-front analysis on red and IR reflections. 
	\item Qualified and adapted existing drive electronics for use with MEMS adaptive optics device.
	
	\end{itemize}
	
\item 
\workexp{Mathematics Tutor}{SBCC, Santa Barbara CA}{Aug. 2014 - July 2016}{}
\\[-0.3cm]
	\begin{itemize}\itemsep \isep
	\item Drop-in tutor for Advanced Math Lab (all levels), saw 5-50 students per day.
	\item Gateway tutor for Algebra, Calculus, and Linear Algebra. Hosted 1-2 hour private and group sessions. Gave lessons, review sessions, and supplemental problem sets.
	\item Functioned as TA through in-class tutoring, contribution to lectures, and exam consultations.
	\item Mentored new tutors through consultation and workshops and developed problem solving worksheets and heuristics for students.
	\end{itemize}

\item
\workexp{PCB Layout Engineer}{Green Light Props, Santa Barbara CA}{Feb. 2014 - June 2015}{}
\\[-0.3cm]
	\begin{itemize}\itemsep \isep
	\item Company to develop smart LED dance props.
	\item Designed PCB with an ARM-based chip using an 802.15.4 radio, 3-axis accelerometer, LED driver, and USB charging system.
	\item Developed schematics and layouts for two-layer high speed PCBs, Implemented layouts in coordination with manufacturers and suppliers, Ensured layout design compliance with manufacturing requirements.
	\item Maintained documentation of PCB layout and fabrication and performed system checks and tests.
	\end{itemize}
\item
\workexp{Co-Owner}{Lucidity Festivals LLC, Santa Barbara CA}{Jan. 2012 - Present}{}
\\[-0.3cm]
	\begin{itemize}\itemsep \isep
	\item Partner in worker-owned event production company.
	\item Pioneered group decision-making processes, maintained operating agreement, authored orientation materials and procedure handbook.
	\item Holds ongoing roles for annual 5000 person festival. Liaison with County Fire Dept., author of relevant permits.
	\item Responsibilities include material and personnel deployment, inventory management, and  budgeting.
	\end{itemize}
\end{itemize}
%-----------------------------------------------------------

%------------Programming Proficiency------------------

\resheading{\textbf{Technical Skills} }\\[\lsep]
\begin{itemize}
%these will all be on the same line, include a whitespace at the end of each list
\noindent \textbf{Languages:} (Java, C/C++, Python, SQL, MIPS)
\textbf{Tools:} (git, Unix, CAD, MATLAB, LabVIEW)
\end{itemize} 
%-----------------------------------------------------------


%------Other Interests------------------------------------

%\resheading{\textbf{Other Interests} }\\[\lsep]
%\\[0.2cm]
%\indent \begin{tabular}{  l  r   r } 
%\indent Music; classical, folk; guitar, mandolin & \indent  & \indent \indent Oct. 1999\\
%\indent Fire dance and juggling teacher/performer: & \indent https://youtube.com/rydubbin  & \indent  \indent Nov. 2009\\
%\indent Rock climber, hiker, and outdoorsman & \indent  & \indent \indent Dec. 2015\\
%\end{tabular}



%-----------------------------------------------------------

\end{document}